### 2021-04-26 sections/queueing_model/main.tex
Write details of the Markov-chain model
- Define the model
- Define state space
- Define transition matrix and state-mapping function

>>>>

% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of patient.

The model consists of two types of individuals; class 1 and class 2.
Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Class 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed to the next waiting zone only when the number of 
individuals in the next system (in waiting zone 1 and in service) is less than a 
pre-determined threshold \(T\).
When the threshold is reached, all class 2 individuals that arrive will remain 
\textit{``blocked''} in the buffer centre until the number of people in the 
system is reduced below \(T\).

% TODO: Possibly worth including the diagram of the queueing model here

In order to model such queueing system a Markov chain model was used.
Markov chains are a special kind of memoryless stochastic systems where the 
outcome of the next iteration depends only on the current state
~\cite{kemeny1976markov}. 
The way such models are formulated is through a directed graph where each vertex
is consider a state of the system and each edge represents the transition rate
between its two linking vertices.
The states of the Markov chain are denoted by \((u,v)\) where:

\begin{itemize}
    \item \(u\) = number of individuals blocked
    \item \(v\) = number of individuals either in waiting zone 1 or in the
    service centre
\end{itemize}

The state space of the Markov chain \(S\) is defined as the union between
\(S_1\) and \(S_2\), where \(S_1\) represents the set of states where the total 
number of individuals is less than \(T\) and \(S_2\) the set of states where the
total number of individuals is greater than \(T\).

\begin{align}
    S(T) =& S_1(T) \cup S_2(T) \text{ where:} \nonumber \\
    S_1(T) =& \left\{(0, v)\in\mathbb{N}_0^2 \; | \; v < T \right\} 
    \label{eq:state_space} \\
    S_2(T) =& \{(u, v)\in\mathbb{N}_0^2 \; | \; v \geq T \} \nonumber
\end{align}

The transition matrix \(Q\) of the Markov chain consists of the transition rates
between the numerous states of the model. Every entry \( q_{i,j} = 
q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).
The entries of \(Q\) can be calculated using the state-mapping function 
described in \ref{eq:markov_transition_rate}:

\begin{equation} \label{eq:markov_transition_rate}
    q_{i, j} = 
    \begin{cases}
        \Lambda, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
        v_i < \text{t} \\
        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
        v_i \geq \text{t} \\
        \lambda_2, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (-1,0) \\
        v_i \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
        \textbf{ and } v_i = T \leq C \\
        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } v_i > C 
        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) \textbf{ and } 
        v_i = T > C\\
        -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
        0, & \textbf{otherwise}
    \end{cases}
\end{equation}

% \input{sections/queueing_model/general-markov-model/main.tex}

In order to acquire an exact solution of the problem a slight adjustment needs to 
be considered. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or for the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) needs to be constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of people \(N\) 
that can be in the system and a maximum allowed number of people \(M\) that can
be blocked in the buffer centre:

\begin{equation}
    \tilde S = \left\{ (u, v) \in S\;| u \leq M, v\leq N \right\}
\end{equation}

\subsection{Performance Measures}

\subsection{Example}
